# Data Programming {-}

  * [R](https://www.r-project.org/)
      
      + To download R, choose a [CRAN mirror](https://cran.r-project.org/mirrors.html) closest to your geographic location.
      + In order to build R packages, you should also download the latest recommended version of [Rtools](https://cran.r-project.org/bin/windows/Rtools/). Currently, the latest recommended version is `Rtoools35.exe`.
      + During the installation of Rtools, you may need to add in `"C:\Rtools\mingw_64\bin;"` to the path.
      
  * [R Studio](https://www.rstudio.com/products/rstudio/download/#download)
  
      + R Studio is an integrated development environment (IDE) for R. After downloading R Studio, you should be able to type the following command at the console to download some common R packages for data analysis and visualization.
      
```{r eval=FALSE}
install.packages(c("dplyr", "tidyr", "ggplot2", "esquisse", "stats", "xtable"))
```
## Cleaning and Reshaping Data

```{r, results='asis', warning=FALSE, message=FALSE, cache=TRUE}
library(reshape2)
library(tidyr)
library(xtable)
library(stringr)
library(knitr)
options(kableExtra.latex.load_packages = FALSE)
library(kableExtra)
library(pander)


#original data is organized by id/trial (two locations per entry)
game <- data.frame(id = c(rep("X",3), rep("Y",3), rep("Z",3)),
           trial = rep(c(1,2,3), 3),
           location_A = round(rnorm(9, mean = 0, sd = 1), 1),
           location_B = round(rnorm(9, mean = 0, sd = 1), 1))

# reshape data from wide to long (each entry is unique by id/trial/location)
game_long <- melt(game, id = c("id","trial"), value.name = "score")
game_long$variable <- str_sub(game_long$variable,-1,-1)
colnames(game_long)[3] <- "location"

# reshape data back to wide (same as original data)
game_wide <- dcast(game_long, id + trial ~ location, value.var = "score")
# reshape data into even wider form (one entry per id with 6 value columns: 2 locations X 3 trials)
game_wider <- dcast(game_long, id ~ location + trial, value.var = "score")

# using tidyr and dplyr to reshape data
game_long2 <- game %>% gather(label, score, location_A, location_B) %>%
    separate(label, c("label_p1","location"), sep = "_") %>%
    dplyr::select(-label_p1)

game_wide2 <- game_long2 %>% spread(location, value = score)

#unite() function creates the location X trial combinations first in long format # then apply the spread() function to reshape into wide format
#just like in game_wide, each entry in game_wide2 is unique by id
game_wider2 <- game_long2 %>% unite(location_trial, location, trial) %>%
    spread(location_trial, value = score)

#xtable method
#print(xtable(game, caption = "Wide Data Listed by Person/Trial (Scores by Location)"), type="html")

#kable method
#kable(game, caption = "Wide Data Listed by Person/Trial (Scores by Location)", booktabs = TRUE) %>%
#    kable_styling(latex_options = c("hold_position"))

#pander method (most flexible)
pandoc.table(game, caption = "(\\#tab:wide) Wide Data Listed by Person/Trial (Scores by Location)")
```

```{r, results='asis', warning=FALSE, message=FALSE, cache=TRUE}
pandoc.table(game_wider, caption = "(\\#tab:wider) Wider Data Listed by ID (Scores by Location/Trial)")
```

```{r, results='asis', warning=FALSE, message=FALSE, cache=TRUE}
pandoc.table(game_long, caption = "(\\#tab:long) Long Data")
```
  
  * [Data Wrangling with dplyr and tidyr](https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf)



## Regular Expressions

  * [Regular Expressions in R](https://stringr.tidyverse.org/articles/regular-expressions.html)
  
  * [Basic Regular Expressions in R Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2016/09/RegExCheatsheet.pdf)

# Literate Programming {-}

## LaTeX

  * [MiKTeX](https://miktex.org/download)
      - First, download MiKTeX. Choose the version corresponding to your operating system (Windows, Mac, or Linux). Skip this step if you decide to use ShareLaTeX, which is an online LaTeX editor and does not require your computer to have underlying LaTeX packages via MiKTeX.
      - Recommended, download the basic installer, which will download other uninstalled packages on the fly on an as-needed basis. If you want to download all packages, you can choose the Net Installer, but this may take up a lot of space.
      
  * [Review of LaTeX Editors](https://blog.typeset.io/the-only-latex-editor-guide-youll-need-in-2018-e63868fae027)
  
      - [Overleaf/ShareLaTeX](https://www.overleaf.com/)
      - [TeXstudio](https://www.texstudio.org/)
      - [LyX](https://www.lyx.org/)
  
  * [LaTeX Guides](https://guides.library.harvard.edu/overleaf/latex)
  
  * [LaTeX Cheat Sheet](https://www.nyu.edu/projects/beber/files/Chang_LaTeX_sheet.pdf)
  
  * Q and A:
  
      - [Reference File in Parent Folder](https://tex.stackexchange.com/questions/29172/link-to-file-in-the-parent-folder)

## Beamer

  Beamer is a LaTeX class for presentations.
  

## knitr (R + LaTeX)

  * [Using knitr in LyX](http://www.chrisbilder.com/stat850/LyXLaTeX/knitr/LyX-knitr1per.pdf)
  
  * [Configure Texstudio to use knitr](https://www.pauljhurtado.com/teaching/software.html)

  * [Create LaTeX Tables with kable](https://haozhu233.github.io/kableExtra/awesome_table_in_pdf.pdf)
      + To avoid a incompatibility warning about the LaTeX `xcolor` package, place `options(kableExtra.latex.load_packages = FALSE)` in your R chunk before `library(kableExtra)`. See Hao Zhu's explanation in page 4 of the link above.
  
  * [kableExtra Vignettes](http://haozhu233.github.io/kableExtra/)
      + vignettes for using outputting tables from R into HTML, LaTeX, and Word

  * [xtable and stargazer Examples](https://rpubs.com/pankil/84526)
  
  * [pander Tutorial](https://rapporter.github.io/pander/#pander-an-r-pandoc-writer)
  
## R Markdown

  * [Markdown Reference](https://github.com/adam-p/markdown-here/wiki/Markdown-Cheatsheet)
  * [R Markdown Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf)
  * [Writing a Reproducible Paper in R Markdown](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=3175518)
  
## R Bookdown

  * [Authoring Books with R Bookdown](https://bookdown.org/yihui/bookdown/)
  
  * [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/)
  
  * [Writing Thesis with Bookdown](https://eddjberry.netlify.com/post/writing-your-thesis-with-bookdown/)
    + Section on outputting into Microsoft Word using `bookdown::preview_chapter()`

## Rmd to MS Word

  * [Rmd to docx](https://rmarkdown.rstudio.com/articles_docx.html)
  
  * [Discussion on Using knitr for Word output](https://community.rstudio.com/t/nice-tables-when-knitting-to-word/3840)
  
# Version Control {-}

  * [Git](https://git-scm.com/downloads)
  
  * Github
  
  * [Best Practices Using Github in RStudio](http://r-pkgs.had.co.nz/git.html)
  
  * [Tutorial on Git for Behavioral Sciences](https://vuorre.netlify.com/pdf/2017-Vuorre-Curley.pdf)
  
  * [Github and R](https://happygitwithr.com/)
