--- 
title: "AP Research Syllabus"
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: article
bibliography: [book.bib, packages.bib]
biblio-style: "apalike"
csl: apa.csl
link-citations: yes
github-repo: apscholar/ap-research-syllabus
description: "This notebook includes a syllabus and detailed course schedule for AP Research"
always_allow_html: yes
---

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=FALSE, dev='png')
mon <- as.Date("2016-08-15")
# fri <- as.Date("2016-01-08")

advdate <- function(obj, adv) {
 tmon <- obj + 7*(adv-1)
 tfri <- obj + 4 + 7*(adv-1)
 tmon <- format(tmon, format="%m/%d")
 tfri <- format(tfri, format="%m/%d")
 zadv <- sprintf("%02d", adv)
 tmp <- paste("Week ",zadv,sep='',", ", tmon," - ",tfri)
 return(tmp)
}

library(RefManageR)
# library(knitcitations)
# library(rcrossref)
bib <- ReadBib("book.bib")
BibOptions(bib.style = "authoryear", style="markdown", first.inits=TRUE, max.names = 4, check.entries = FALSE)

```
# Course Description
**Prerequisite:** AP Seminar  
AP Research is a one-year course that culminates in a 4000- to 5000-word academic paper and a 15- to 20-minute presentation with oral defense. Students will learn the process of academic research as well as industry-aligned research tools. Depending on the students' research topics, research methods aligned with the AP Statistics curriculum may be integrated into mini-workshops.
